### 2019-04-09 paper/paper.tex
some formatting

\begin{IEEEkeywords}
JavaScript; software ecosystem analysis; Node.js; replication
\end{IEEEkeywords}

\section{Introduction}
Software ecosystems are environments that form as projects evolve in parallel,
becoming interconnected as contexts and dependencies span companies and communities \cite{LUNGU2010264}. 
Research on these systems has increased rapidly in the recent past \cite{Manikas:2017}, investigating
their characteristics and behaviour as they develop \cite{Manikas:2013}. Understanding how software
ecosystems form and change is important from both a software as well as a business standpoint\cite{Messerschmitt},
and is valuable for informing developers how technologies are used over time \cite{Serebrenik:2015}. 
An understanding of software ecosystems can inform decisions on when to adopt frameworks and how long
to support them, as well as provide insight into how changes to software propagate throughout the community \cite{Wittern:2016}.
Additionally, determining the characteristics of software ecosystems 
can help clarify why some frameworks flourish while others fail, and guide 
developers in the creation of new tools\cite{Serebrenik:2015}. Furthermore, 
because software projects are overwhelmingly a collaborative effort, a complete
understanding of a single project often requires knowledge of the ecosystem supporting it\cite{Blincoe:2015}.

>>>>

\begin{IEEEkeywords}
JavaScript; Node.js; node package manager; software ecosystem analysis
\end{IEEEkeywords}

\section{Introduction}
Software ecosystems are environments that form as projects develop in parallel,
becoming interconnected as contexts and dependencies span companies and communities \cite{LUNGU2010264}. 
Research on these systems has increased rapidly in the recent past \cite{Manikas:2017}, investigating
their characteristics and behaviour as they develop \cite{Manikas:2013}. Understanding how software
ecosystems evolve is important from both a software as well as a business standpoint\cite{Messerschmitt},
and is valuable for informing developers how technologies are used over time \cite{Serebrenik:2015}. 
An understanding of software ecosystems can inform decisions on when to adopt frameworks and how long
to support them, as well as provide insight into how changes to software propagate throughout the community \cite{Wittern:2016}.
Additionally, determining the characteristics of software ecosystems 
can help clarify why some frameworks flourish while others fail, and guide 
developers in the creation of new tools\cite{Serebrenik:2015}. Furthermore, 
because software projects are overwhelmingly a collaborative effort, a complete
understanding of a single project often requires knowledge of the ecosystem supporting it\cite{Blincoe:2015}.
